\subsection{The Need for Business Requirements in Nowcasting}

In the realm of meteorology, the importance of accurate and timely weather
forecasts cannot be overstated, especially for short-term (3-6 hours) and
immediate forecasts known as nowcasting (<3 hours). While automated weather
stations are equipped with advanced technology for meteorological data
processing—such as data collection, ETL (Extract, Transform, Load) processes,
and analysis—the business processes surrounding these forecasts remain largely
manual. This disparity between technological capability and operational
efficiency hampers the overall effectiveness of weather prediction and response.

\subsubsection*{Current State of Technology in Meteorological Processing}
Automated weather stations have revolutionized the field of meteorology with
their ability to continuously monitor and process vast amounts of weather data.
These stations employ sophisticated sensors and data processing algorithms to
collect, transform, and analyze meteorological data in real-time. The
integration of these technologies enables accurate and rapid weather
observations, which are critical for creating reliable forecasts.

\subsubsection*{Challenges in Business Processes}
Despite the technological advancements in data processing, many business
processes in meteorological services are still conducted manually. This includes
constructing reports for abnormal weather phenomena using tools like Microsoft
Word and sending email alerts manually. Such manual processes introduce
significant delays in issuing alerts and hinder the responsiveness of nowcasting
systems. The delay in alert dissemination not only affects the ability to
provide timely warnings but also impacts the overall efficiency of weather
forecasting operations.

\subsubsection*{The Need for Automation and Database Handling}
To bridge the gap between technological capabilities and operational efficiency,
there is a pressing need to automate business processes in meteorological
services. An automated system for handling these processes would significantly
enhance the speed and accuracy of weather alerts and nowcasting.

The system should support \textbf{dynamic fields for data input}, allowing
flexibility in capturing various types of weather data and abnormal phenomena.
This dynamic data collection capability ensures that the system can adapt to the
diverse and evolving nature of meteorological observations, facilitating the
accurate recording of critical data points.

Incorporating \textbf{templates for report generation} can streamline the
creation of consistent and standardized reports, reducing the time and effort
required for manual report construction. Template-based reporting ensures that
essential information is presented uniformly, making it easier to interpret and
act upon the data provided.

\textbf{Automating the process of report creation and email distribution}
ensures that alerts are sent out promptly and accurately, minimizing human error
and delays. Automated report creation and distribution systems can trigger
alerts based on predefined criteria, ensuring that relevant stakeholders receive
timely notifications of abnormal weather conditions.

A \textbf{robust database system} is essential to handle the storage, retrieval,
and management of data conducted in meteorological business process. This
database should provide a reliable platform for data-driven decision-making.
Effective database management enables efficient data organization, ensuring that
critical information is readily accessible for analysis and reporting.

In conclusion, the integration of automated processes and advanced database
management systems is crucial for enhancing the efficiency and effectiveness of
nowcasting. By addressing the current limitations in business processes,
meteorological services can significantly improve their ability to provide
timely and accurate weather forecasts, ultimately safeguarding lives and
property.


\subsection{Functional Requirement}

In the initial phase of the data processing workflow, \textbf{data ingestion}
emerges as a pivotal undertaking, wherein data is systematically amassed from a
spectrum of heterogeneous sources, spanning from \textbf{Application Programming
Interfaces (APIs)} to repositories housing \textbf{government data}. This
foundational process assumes paramount significance as it sets the groundwork
for the acquisition of an extensive array of datasets essential for
comprehensive analytical endeavors.

Following data ingestion, the subsequent stage revolves around \textbf{data
    storage} and \textbf{management}. This facet encompasses the orchestration
    of repositories, potentially ranging from conventional databases to more
    contemporary constructs like \textbf{data lakes}. Such infrastructural
    modalities afford robust frameworks that adeptly cater to the exigencies
    imposed by the management of copious volumes of data, thereby ensuring
    efficiency and efficacy in handling data resources.

Concomitant with data management, \textbf{data analysis} and
\textbf{visualization} procedures are meticulously tailored to cater to the
discerning requirements of stakeholders entrenched within the meteorological
domain and academic research milieu. These analytical tools serve as
indispensable instruments, facilitating granular scrutiny and cogent
interpretation of meteorological datasets, thereby fostering informed
decision-making and scholarly inquiry.

Facilitating seamless interoperability with external platforms and augmenting
the system's functionality through synergistic engagement with \textbf{APIs}
represent pivotal components of the overarching operational paradigm. Such
integrative endeavors engender an ecosystem conducive to harmonious interactions
with an array of technological adjuncts, thereby amplifying the system's utility
and efficacy.

Furthermore, the system incorporates robust \textbf{user management} protocols
and \textbf{access control mechanisms} to ensure the sanctity of data assets,
conferring access exclusively to duly authorized personnel. By meticulously
safeguarding data integrity and confidentiality, these provisions engender an
environment predicated upon trust and accountability, thereby fortifying the
organizational edifice.

Finally, the culminating facets of \textbf{reporting} and \textbf{alerting
    functionalities} emerge as indispensable conduits for the expeditious
    dissemination of critical insights and information to an array of
    stakeholders, encompassing end-users, organizational hierarchies, and
    strategic decision-makers. These functionalities serve as conduits for the
    expeditious transmission of salient information, thereby empowering
    stakeholders to navigate dynamic operational landscapes with acumen and
    alacrity.

\subsection{Non-Functional Requirements}

In the realm of technological platforms, the facet of \textbf{Reliability}
stands as a cornerstone, necessitating unwavering commitment towards ensuring
persistent high availability and steadfast operational stability. Paramount to
this pursuit is the unyielding dedication towards upholding \textbf{data
integrity}, \textbf{security}, and \textbf{privacy} as cardinal imperatives,
safeguarding both user information and system data against potential
vulnerabilities and breaches.

Moreover, the imperative of \textbf{Scalability} looms large, compelling the
platform to confront the exigencies posed by burgeoning volumes of data. In this
regard, an adept embrace of \textbf{cloud-native technologies} and the paradigm
of \textbf{containerization}, exemplified by stalwarts such as Docker and
Kubernetes, emerges as indispensable. Such technological modalities proffer the
requisite infrastructure agility, facilitating seamless and expedient scaling of
both infrastructure and applications alike, thereby ensuring commensurate
responsiveness to evolving operational demands.

Further accentuating the discourse, the criterion of \textbf{Performance}
assumes primacy, necessitating the provision of expeditious data processing and
analysis capabilities. This imperative is underscored by the imperatives of
real-time decision-making imperatives and the imperative of managing large-scale
data operations with finesse and alacrity.

In tandem, the imperative of \textbf{Usability} assumes paramount significance,
underscoring the imperative of furnishing an interface that is as intuitive as
it is user-friendly. A bespoke interface, meticulously tailored to cater to the
diverse exigencies of disparate user cohorts, stands as a testament to the
platform's commitment towards ensuring unfettered ease of access and usability.

Moreover, the aspect of \textbf{Security} mandates robust fortifications,
encompassing both data protection protocols and stringent access control
mechanisms. This multifaceted approach is calibrated to thwart the machinations
of unauthorized access and avert the specter of potential data breaches, thereby
undergirding the sanctity of the platform's operational integrity.

Simultaneously, adherence to \textbf{Compliance} imperatives emerges as
non-negotiable, enjoining scrupulous conformity with a panoply of regulatory
stipulations, data privacy statutes, and overarching compliance requisites. Such
fidelity towards regulatory benchmarks serves as an indispensable bulwark,
ensuring that the platform operates within the hallowed precincts of legal and
ethical propriety.

Lastly, expounding upon the contours of \textbf{scaling technology and
    infrastructure}, the platform espouses an ethos predicated upon the tenets
    of \textbf{cloud-native architectures} and containerization technologies.
    This strategic pivot affords the platform the requisite nimbleness,
    facilitated by the judicious employment of auto-scaling capabilities and the
    elastic resources proffered by cloud platforms. Furthermore, the adoption of
    a \textbf{microservices architecture} and the decoupling of components augur
    well for bolstering the platform's resilience and flexibility, enabling
    independent scaling of discrete services or modules, and thus engendering a
    paradigm of operational dynamism and adaptability.

\subsection{Data Requirements}
In the intricate domain of radar data management, the foundational phase
commences with an exhaustive \textbf{cleaning process}. This pivotal endeavor is
indispensable, serving as the vanguard against the encroachment of
\textbf{noise} and extraneous data, thereby ensuring the veracity and
reliability of the data corpus. The imperative of cleansing radar files assumes
paramount significance, poised as it is to ready them for the rigors of more
intricate processing and analysis, which constitute linchpins in facilitating
accurate meteorological appraisals.

Subsequent to the meticulous cleansing regimen, the radar data traverses a
sophisticated trajectory, wherein it becomes ensconced within a nuanced
\textbf{processing routine}. At this juncture, specialized algorithms assume the
mantle, orchestrating a symphony of analyses to distill meaningful patterns and
insights from the data trove. This transformative phase is pivotal, transmuting
raw data into actionable intelligence, thereby furnishing decision-makers with a
bedrock of dependable insights.

Post the crucible of processing, the data finds sanctuary within the confines of
\textbf{blobs} nestled within an object storage apparatus, typically epitomized
by \textbf{Minio}. This methodical selection of storage modality is predicated
upon its inherent scalability and facile accessibility, attributes that are
deemed indispensable in wrangling the prodigious volumes of data bequeathed by
radar systems. Moreover, the architecture of blob storage engenders a milieu
conducive to expeditious data retrieval and management, adeptly accommodating
the dynamic access patterns germane to meteorological exigencies.

In a bid to further fortify the edifice of data handling efficacy, the apparatus
embraces the instantiation of a \textbf{caching mechanism}. This strategic
deployment bestows upon the system the capability to temporarily harbor recently
accessed data, thereby effectuating a palpable reduction in retrieval latencies.
This feature assumes outsized significance, particularly in scenarios of
heightened exigency, such as severe weather events, wherein the expeditious
access to data assumes the mantle of existential import.

The hallowed precincts of processed and stored radar data resonate with a
multifaceted utility, traversing a panoply of applications. Meteorologists,
ensconced within the annals of weather forecasting and climate modeling, find
themselves inexorably tethered to this fount of data-driven insights.
Concurrently, the pantheon of emergency response entities stands as ardent
beneficiaries, drawing succor from the real-time data streams that undergird
effective decision-making in the crucible of weather-related emergencies.
Furthermore, the expansive vista of scientific inquiry finds solace in this rich
tapestry of data, wielding it as a potent instrument in unraveling the enigmatic
contours of climate patterns and atmospheric dynamics.
